---
title: "Analysis_UVA"
output: html_notebook
---

Creating the GLM model:
```{r}
MultiVar_HospAfterED <- function(All_ED_df) {

library(geepack)
library(broom)
library(dplyr)
# Turns all categorical or binary predictors into factor type data
All_ED_df$race_ethnicity <- as.factor(All_ED_df$race_ethnicity)
All_ED_df$age_at_covid <- as.numeric(All_ED_df$age_at_covid)
#should be gender_concept_name
All_ED_df$sex <- as.factor(All_ED_df$sex)
All_ED_df$DiabetesComplicated_before_or_day_of_covid_indicator <- as.factor(All_ED_df$DiabetesComplicated_before_or_day_of_covid_indicator)
#All_ED_df$ASTHMA_before_covid_indicator <- as.factor(All_ED_df$ASTHMA_before_covid_indicator)
All_ED_df$HIVINFECTION_before_or_day_of_covid_indicator <- as.factor(All_ED_df$HIVINFECTION_before_or_day_of_covid_indicator)
All_ED_df$CONGESTIVEHEARTFAILURE_before_or_day_of_covid_indicator <- as.factor(All_ED_df$CONGESTIVEHEARTFAILURE_before_or_day_of_covid_indicator)
All_ED_df$MALIGNANTCANCER_before_or_day_of_covid_indicator <- as.factor(All_ED_df$MALIGNANTCANCER_before_or_day_of_covid_indicator)
#All_ED_df$end_stage_renal_disease_observation_before_covid_indicator <- as.factor(All_ED_df$end_stage_renal_disease_observation_before_covid_indicator)
All_ED_df$OBESITY_before_or_day_of_covid_indicator <- as.factor(All_ED_df$OBESITY_before_or_day_of_covid_indicator)
All_ED_df$CHRONICLUNGDISEASE_before_or_day_of_covid_indicator <- as.factor(All_ED_df$CHRONICLUNGDISEASE_before_or_day_of_covid_indicator)
#All_ED_df$data_partner_id <- as.factor(All_ED_df$data_partner_id)
#All_ED_df$REMDISIVIR_during_covid_hospitalization_indicator <- as.factor(All_ED_df$REMDISIVIR_during_covid_hospitalization_indicator)

# Sets white NH as the reference group for race/ethnicity variable
All_ED_df$race_ethnicity <- relevel(All_ED_df$race_ethnicity, ref="White Non-Hispanic")
#All_ED_df$data_partner_id <- as.factor(All_ED_df$data_partner_id)

# Multivar GEE Regression (x=race/ethnicity, age, sex, diabetes, asthma, HIV, CHF, cancer, end stage renal disease, obesity, and chronic lung disease, y=hospitalization within 30 days of ED)
#the original response variable was ED_then_Hospitalized_within_30_days
gee_model <- geeglm(ED_then_Immediately_Hospitalized ~ race_ethnicity + age_at_covid + sex + DiabetesComplicated_before_or_day_of_covid_indicator + HIVINFECTION_before_or_day_of_covid_indicator + CONGESTIVEHEARTFAILURE_before_or_day_of_covid_indicator + MALIGNANTCANCER_before_or_day_of_covid_indicator + OBESITY_before_or_day_of_covid_indicator +  CHRONICLUNGDISEASE_before_or_day_of_covid_indicator, data = All_ED_df, id = person_id, family = binomial, corstr = "independence")

# Summary of the regression
print(summary(gee_model))

## Prints out odds ratios and 95% CI
#print(exp(cbind(OR = coef(gee_model), confint(gee_model))))

# Create table of model results
# Gives the regression output as a table
mod_tbl <- broom::tidy(gee_model, conf.int = TRUE, exponentiate = TRUE)
#mod_eval <- broom::glance(gee_model)
#print(mod_eval)
mod_tbl <- mod_tbl %>% rename(OR = estimate)

return(mod_tbl)

}
```
UVA Data tagged temporally modeling:
```{r}
#this is where the Patient Final Table is read in
N3C_tags = read.csv("Filtered_Patient_Final_Table_S1_N3C_Tags (4).csv")
```

```{r}
model1 <- MultiVar_HospAfterED(N3C_tags)
```
UVA Data tagged with Principal Diagnosis modeling:
```{r}
UVA_tags = read.csv("Filtered_Patient_Final_Table_S1_UVA_Tags (3).csv")
model1_2 <- MultiVar_HospAfterED(UVA_tags)
```

```{r}
EDCohort_S1_ForrestPlot <- function(EDCohort_S1_HospAfterED) {
    
library(tidyverse)
library(ggplot2)

df_full = EDCohort_S1_HospAfterED

# Does some cleaning of the dataframe
df_full <- df_full %>% 
    select(-statistic, -std.error) %>%
    mutate(`Pval_Signif`=ifelse(p.value<0.05, "Significant", "Non-Significant")) %>%
    mutate(term=ifelse(term=="race_ethnicityAsian Non-Hispanic", "Asian NH", term)) %>%
    mutate(term=ifelse(term=="race_ethnicityBlack or African American Non-Hispanic", "Black/AA NH", term)) %>%
    mutate(term=ifelse(term=="race_ethnicityHispanic or Latino Any Race", "Hispanic/Latino", term)) %>%
    mutate(term=ifelse(term=="age_at_covid", "Age", term)) %>%
    mutate(term=ifelse(term=="sexMALE", "Sex (Male)", term)) %>%
    mutate(term=ifelse(term=="DiabetesComplicated_before_or_day_of_covid_indicator1", "Diabetes (Complicated)", term)) %>%
#    mutate(term=ifelse(term=="ASTHMA_before_or_day_of_covid_indicator1", "Asthma", term)) %>%
    mutate(term=ifelse(term=="HIVINFECTION_before_or_day_of_covid_indicator1", "HIV Infection", term)) %>%
    mutate(term=ifelse(term=="CONGESTIVEHEARTFAILURE_before_or_day_of_covid_indicator1", "Congestive Heart Failure", term)) %>%
    mutate(term=ifelse(term=="MALIGNANTCANCER_before_or_day_of_covid_indicator1", "Malignant Cancer", term)) %>%
#    mutate(term=ifelse(term=="end_stage_renal_disease_observation_before_or_day_of_covid_indicator1", "End Stage Renal Disease", term)) %>%
    mutate(term=ifelse(term=="OBESITY_before_or_day_of_covid_indicator1", "Obesity", term)) %>%
    mutate(term=ifelse(term=="CHRONICLUNGDISEASE_before_or_day_of_covid_indicator1", "Chronic Lung Disease", term))

# Shorter df for the forest plot: comment out first line for shortened forrest plot (without comorb), comment out second line for full forrest plot (with comorb); not relevant in the S1 models with no SDoH
df = df_full
#df = df_full[2:15, ]

# Creates color scheme for p value significance
SigCols <- c(`Non-Significant`="skyblue2", `Significant`="orange2")

# Creates forest plot of OR values
forest_plot <- ggplot(data=df, aes(y=term, x=OR, xmin=conf.low, xmax=conf.high, color=Pval_Signif)) + geom_point() + geom_errorbarh(height=.1) + scale_color_manual(values=SigCols) + labs(x='Odds Ratio (OR)', y = 'Variable', color='p-Value Significance (< .05)') + geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) + theme_classic()+coord_cartesian(xlim=c(0, 3))

#print(forest_plot)

# Rename df column [old way: arrange(desc(abs((1-OR))))]
df_full = df_full %>%
    arrange(desc(OR))

return(forest_plot)

}
```

```{r}
plot1 = EDCohort_S1_ForrestPlot(model1)
plot1 +theme(axis.text=element_text(size=12),axis.title=element_text(size=14),legend.text=element_text(size=12),legend.title=element_text(size=12, face="bold"),legend.position = "top")
```
```{r}
plot1 = EDCohort_S1_ForrestPlot(model1_2)
plot1 +theme(axis.text=element_text(size=12),axis.title=element_text(size=14),legend.text=element_text(size=12),legend.title=element_text(size=12, face="bold"),legend.position = "top")
```
```{r}
plot1 = EDCohort_S1_ForrestPlot(model1_2)
plot1 + labs(title="ED Cohort (UVA tagged) & Hosp. after ED: ORs by Predictor")
```
ED Outcomes for the two UVA Cohorts
```{r}
ED_OutcomeCounts <- function(HI_ED_S3_Transforms) {
    
library(tidyverse)
library(geepack)
library(broom)
library(gtsummary)
library(labelled)

Sum_df = HI_ED_S3_Transforms
# Turns all categorical or binary predictors into factor type data
Sum_df$race_ethnicity <- as.factor(Sum_df$race_ethnicity)
Sum_df$ED_then_Hospitalized <- as.factor(Sum_df$ED_then_Immediately_Hospitalized)
Sum_df$COVID_patient_death_indicator <- as.factor(Sum_df$COVID_patient_death_indicator)

# Labels the variable names 
var_label(Sum_df) <- list(race_ethnicity="Race/Ethnicity", ED_then_Immediately_Hospitalized="Hospitalization after ED", COVID_patient_death_indicator="Patient Death")

Sum_df <- Sum_df %>% select(race_ethnicity, ED_then_Immediately_Hospitalized, COVID_patient_death_indicator)
print(Sum_df)
levels(Sum_df$ED_then_Immediately_Hospitalized) <- list(N = "0", Y = "1")
levels(Sum_df$COVID_patient_death_indicator) <- list(N = "0", Y = "1")

#print(str(Sum_df))

print(tbl_summary(Sum_df, by=race_ethnicity) %>% italicize_levels() %>% add_overall() %>% add_p() %>% bold_p())

tbl <- tbl_summary(Sum_df, by=race_ethnicity) %>% italicize_levels() %>% add_overall() %>% add_p() %>% bold_p() %>% as_tibble()

return(tbl)

}
```

```{r}
ED_OutcomeCounts(N3C_tags)
```
```{r}
ED_OutcomeCounts(UVA_tags)
```

Calculates the average number of comorbidities in the temporally tagged UVA data
```{r}
comorb_N3C = N3C_tags[c("person_id","race_ethnicity","DiabetesComplicated_before_or_day_of_covid_indicator","HIVINFECTION_before_or_day_of_covid_indicator","CONGESTIVEHEARTFAILURE_before_or_day_of_covid_indicator","MALIGNANTCANCER_before_or_day_of_covid_indicator","OBESITY_before_or_day_of_covid_indicator","CHRONICLUNGDISEASE_before_or_day_of_covid_indicator")]
comorb_N3C = comorb_N3C %>%
  rowwise()%>%
  mutate(total_comorb = sum(c_across(3:8)))%>%
  group_by(race_ethnicity)%>%
  summarise(Comorbidities=mean(total_comorb))
comorb_N3C["Tag"] = "UVA Data TD"
comorb_N3C["race_ethnicity"]=c("Asian NH","Black/AA NH","White NH")
comorb_N3C

```

Calculates the proportions of each comorbidity found in each racial/ethnic group for the temporally tagged UVA data
```{r}
prop_N3C = N3C_tags %>%
  group_by(race_ethnicity) %>%
  summarize(sum_diabetes= sum(DiabetesComplicated_before_or_day_of_covid_indicator),
            sum_HIV = sum(HIVINFECTION_before_or_day_of_covid_indicator),
            sum_CHF = sum(CONGESTIVEHEARTFAILURE_before_or_day_of_covid_indicator),
            sum_MC = sum(MALIGNANTCANCER_before_or_day_of_covid_indicator),
            sum_obese = sum(OBESITY_before_or_day_of_covid_indicator),
            sum_CLD = sum(CHRONICLUNGDISEASE_before_or_day_of_covid_indicator),
            sum_Male = sum(sex=='Male'),
            sum_Female = sum(sex=='Female'))
prop_N3C[,2:9] = apply(prop_N3C[,2:9],2,function(x){x/sum(x)})
prop_N3C["Tag"] = "UVA Data TD"
prop_N3C
```

Sums the number patients for each comorbidity for both UVA Cohorts
```{r}
N3Csums <- N3C_tags %>%
  summarize(sum_diabetes= sum(DiabetesComplicated_before_or_day_of_covid_indicator),
            sum_HIV = sum(HIVINFECTION_before_or_day_of_covid_indicator),
            sum_CHF = sum(CONGESTIVEHEARTFAILURE_before_or_day_of_covid_indicator),
            sum_MC = sum(MALIGNANTCANCER_before_or_day_of_covid_indicator),
            sum_obese = sum(OBESITY_before_or_day_of_covid_indicator),
            sum_CLD = sum(CHRONICLUNGDISEASE_before_or_day_of_covid_indicator),
            sum_Male = sum(sex=='Male'),
            sum_old = sum(age_at_covid>=65))
UVAsums <- UVA_tags %>%
  #summarize(cnt=n()) %>%
  summarize(sum_diabetes = sum(DiabetesComplicated_before_or_day_of_covid_indicator),
            sum_HIV = sum(HIVINFECTION_before_or_day_of_covid_indicator),
            sum_CHF = sum(CONGESTIVEHEARTFAILURE_before_or_day_of_covid_indicator),
            sum_MC = sum(MALIGNANTCANCER_before_or_day_of_covid_indicator),
            sum_obese = sum(OBESITY_before_or_day_of_covid_indicator),
            sum_CLD = sum(CHRONICLUNGDISEASE_before_or_day_of_covid_indicator),
            sum_Male = sum(sex=='Male'),
            sum_old = sum(age_at_covid>=65))
sum_total= rbind(UVAsums, N3Csums)
sum_total
```
Looks at the counts of each racial/ethnic group for the temporally tagged UVA data
```{r}
N3C_tags %>%
  count(race_ethnicity)
```

Calculates the average number of comorbidities in the principal diagnosis tagged UVA data
```{r}
comorb_UVA = UVA_tags[c("person_id","race_ethnicity","DiabetesComplicated_before_or_day_of_covid_indicator","HIVINFECTION_before_or_day_of_covid_indicator","CONGESTIVEHEARTFAILURE_before_or_day_of_covid_indicator","MALIGNANTCANCER_before_or_day_of_covid_indicator","OBESITY_before_or_day_of_covid_indicator","CHRONICLUNGDISEASE_before_or_day_of_covid_indicator")]
comorb_UVA = comorb_UVA %>%
  rowwise()%>%
  mutate(total_comorb = sum(c_across(3:8)))%>%
  group_by(race_ethnicity)%>%
  summarise(Comorbidities=mean(total_comorb))
comorb_UVA["Tag"] = "UVA Data PD"
comorb_UVA["race_ethnicity"]=c("Asian NH","Black/AA NH","White NH")
comorb_UVA
```

Calculates the proportions of each comorbidity found in each racial/ethnic group for the principal diagnosis tagged UVA data
```{r}
prop_UVA = UVA_tags %>%
  group_by(race_ethnicity) %>%
  #summarize(cnt=n()) %>%
  summarize(sum_diabetes = sum(DiabetesComplicated_before_or_day_of_covid_indicator),
            sum_HIV = sum(HIVINFECTION_before_or_day_of_covid_indicator),
            sum_CHF = sum(CONGESTIVEHEARTFAILURE_before_or_day_of_covid_indicator),
            sum_MC = sum(MALIGNANTCANCER_before_or_day_of_covid_indicator),
            sum_obese = sum(OBESITY_before_or_day_of_covid_indicator),
            sum_CLD = sum(CHRONICLUNGDISEASE_before_or_day_of_covid_indicator),
            sum_Male = sum(sex=='Male'),
            sum_Female = sum(sex=='Female'))
prop_UVA[,2:9] = apply(prop_UVA[,2:9],2,function(x){x/sum(x)})
prop_UVA["Tag"] =  "UVA Data PD"
prop_UVA
```

Looks at the counts of each racial/ethnic group for the principal diagnosis tagged UVA data
```{r}
UVA_tags %>%
  count(race_ethnicity)
```

Creating a graph that shows the average number of comorbidities for each cohort.
```{r}
combined = rbind(comorb_UVA,comorb_N3C)
#bringing in data from the Enclave
comorb_N3C2 <- data.frame(race_ethnicity= c("Asian NH","Black/AA NH","White NH"),Comorbidities=c(0.4081,0.7205,0.6804),Tag=c("Data From N3C Enclave","Data From N3C Enclave","Data From N3C Enclave"))
combined = rbind(combined,comorb_N3C2)
```

```{r}
#bar for each ethnic group
#x axis = comorb
#y axis = value
combined$Tag <- factor(combined$Tag, levels=c("Data From N3C Enclave",
                                                    "UVA Data TD",
                                                    "UVA Data PD"))
ggplot(data= combined, aes(x=race_ethnicity,y=Comorbidities, fill=Tag))+
  geom_bar(stat="identity",position=position_dodge())+labs(x="Race/Ethnicity",y="Comorbidities Per Patient",fill="Cohort")+geom_text(aes(label=round(Comorbidities,digits=2)), position=position_dodge(width=0.9), vjust=-0.25)+theme_bw()+theme(axis.text=element_text(size=12),axis.title=element_text(size=14),legend.text=element_text(size=12),legend.title=element_text(size=12, face="bold"),legend.position = "top")
```

Creating a graph that shows the proportion of each racial/ethnic group in each cohort
```{r}
race_ethnicity_N3C = N3C_tags %>% count(race_ethnicity)
race_ethnicity_N3C["Tag"] = "UVA Data TD"
race_ethnicity_N3C["race_ethnicity"] = c("Asian NH","Black/AA NH","White NH")
race_ethnicity_N3C = race_ethnicity_N3C %>% mutate(percent = n/sum(n))
race_ethnicity_UVA = N3C_tags %>% count(race_ethnicity)
race_ethnicity_UVA["Tag"] = "UVA Data PD"
race_ethnicity_UVA["race_ethnicity"] = c("Asian NH","Black/AA NH","White NH")
race_ethnicity_UVA = race_ethnicity_UVA %>% mutate(percent = n/sum(n))
#bringing in data from the Enclave
race_ethnicity_N3C2 <- data.frame(race_ethnicity= c("Asian NH","Black/AA NH","White NH"),n=c(19645,186571,475673),Tag=c("Data From N3C Enclave","Data From N3C Enclave","Data From N3C Enclave"))
race_ethnicity_N3C2 = race_ethnicity_N3C2 %>% mutate(percent = n/sum(n))
```

```{r}
N3C_tags %>% count(race_ethnicity)
```


```{r}
combine1 = rbind(race_ethnicity_N3C,race_ethnicity_UVA)
combine2 = rbind(combine1,race_ethnicity_N3C2)
```

```{r}
combine2$Tag <- factor(combine2$Tag, levels=c("Data From N3C Enclave",
                                                    "UVA Data TD",
                                                    "UVA Data PD"))
ggplot(data = combine2, aes(x=race_ethnicity,y=percent,fill=Tag))+
  geom_bar(stat="identity",position=position_dodge())+geom_text(aes(label=round(percent,digits=2)), position=position_dodge(width=0.9), vjust=-0.25)+labs(x="Race/Ethnicity",y="Proportion",fill="Cohort")+theme_bw()+theme(axis.text=element_text(size=12),axis.title=element_text(size=14),legend.text=element_text(size=12),legend.title=element_text(size=12, face="bold"),legend.position = "top")
```
Creating graphs that show the proportion of each racial/ethnic group for each comorbidity.
Any csv that is read in is from the N3C enclave. These are summary tables of patient data that were approved for release and use in our manuscript.
```{r}
age_N3C = N3C_tags[c("age_at_covid","race_ethnicity")]
age_N3C["Tag"] = "UVA Data TD"
age_UVA = UVA_tags[c("age_at_covid","race_ethnicity")]
age_UVA["Tag"] = "UVA Data PD"
```

```{r}
age_N3C2 = read.csv("age_N3C.csv")
```

```{r}
all_comorb = UVA_tags[c("person_id","race_ethnicity","DiabetesComplicated_before_or_day_of_covid_indicator","HIVINFECTION_before_or_day_of_covid_indicator","CONGESTIVEHEARTFAILURE_before_or_day_of_covid_indicator","MALIGNANTCANCER_before_or_day_of_covid_indicator","OBESITY_before_or_day_of_covid_indicator","CHRONICLUNGDISEASE_before_or_day_of_covid_indicator")]
all_comorb["Tag"] = "UVA Data, PD"
diabetes = all_comorb %>% filter(DiabetesComplicated_before_or_day_of_covid_indicator==1)
all_comorb_N3C = N3C_tags[c("person_id","race_ethnicity","DiabetesComplicated_before_or_day_of_covid_indicator","HIVINFECTION_before_or_day_of_covid_indicator","CONGESTIVEHEARTFAILURE_before_or_day_of_covid_indicator","MALIGNANTCANCER_before_or_day_of_covid_indicator","OBESITY_before_or_day_of_covid_indicator","CHRONICLUNGDISEASE_before_or_day_of_covid_indicator")]
all_comorb_N3C["Tag"] = "UVA Data, TD"
diabetes_N3C = all_comorb_N3C %>% filter(DiabetesComplicated_before_or_day_of_covid_indicator==1) %>% group_by(race_ethnicity) %>% summarize(diabetes_sum = sum(DiabetesComplicated_before_or_day_of_covid_indicator))
diabetes

```


```{r}
prop_N3C2 <- read.csv("comorbs_N3C.csv")
```
```{r}
prop_N3C2["Tag"] = "N3C Enclave"
```



```{r}
prop_UVA["race_ethnicity"] = c("Asian NH","Black/AA NH","White NH")
prop_N3C["race_ethnicity"] = c("Asian NH","Black/AA NH","White NH")
prop_N3C2["race_ethnicity"] = c("Asian NH","Black/AA NH","White NH")
combine1 = rbind(prop_UVA,prop_N3C)
combine2 = rbind(combine1,prop_N3C2)
graph_diabetes = ggplot(data=combine2,aes(x=Tag,y=sum_diabetes, fill=race_ethnicity))+
         geom_bar(stat="identity")+theme_bw()+labs(x="Cohort",y="Proportion of Patients with Diabetes",title="Patients with Diabetes By Cohort and Race/Ethnicity")
graph_diabetes$labels$fill <- "Race/Ethnicity"
graph_diabetes
```
```{r}
graph_HIV = ggplot(data=combine2,aes(x=Tag,y=sum_HIV, fill=race_ethnicity))+
         geom_bar(stat="identity")+theme_bw()+labs(x="Cohort",y="Proportion of Patients with HIV",title="HIV Positive Patients By Cohort and Race/Ethnicity")
graph_HIV$labels$fill <- "Race/Ethnicity"
graph_HIV
```
```{r}
graph_CHF = ggplot(data=combine2,aes(x=Tag,y=sum_CHF, fill=race_ethnicity))+
         geom_bar(stat="identity")+theme_bw()+labs(x="Cohort",y="Proportion of Patients with CHF",title="Patients with Congestive Heart Failure By Cohort and Race/Ethnicity")
graph_CHF$labels$fill <- "Race/Ethnicity"
graph_CHF
```
```{r}
graph_MC = ggplot(data=combine2,aes(x=Tag,y=sum_MC, fill=race_ethnicity))+
         geom_bar(stat="identity")+theme_bw()+labs(x="Cohort",y="Proportion of Patients with Malignant Cancer",title="Patients with Malignant Cancer By Cohort and Race/Ethnicity")
graph_MC$labels$fill <- "Race/Ethnicity"
graph_MC
```
```{r}
graph_obese = ggplot(data=combine2,aes(x=Tag,y=sum_obese, fill=race_ethnicity))+
         geom_bar(stat="identity")+theme_bw()+labs(x="Cohort",y="Proportion of Obese Patients",title="Obese Patients By Cohort and Race/Ethnicity")
graph_obese$labels$fill <- "Race/Ethnicity"
graph_obese
```
```{r}
graph_CLD = ggplot(data=combine2,aes(x=Tag,y=sum_CLD, fill=race_ethnicity))+
         geom_bar(stat="identity")+theme_bw()+labs(x="Cohort",y="Proportion of Patients with Chronic Lung Disease",title="Patients with Chronic Lung Disease By Cohort and Race/Ethnicity")
graph_CLD$labels$fill <- "Race/Ethnicity"
graph_CLD
```
```{r}
graph_CLD = ggplot(data=combine2,aes(x=Tag,y=sum_Male, fill=race_ethnicity))+
         geom_bar(stat="identity")+theme_bw()+labs(x="Cohort",y="Proportion of Male Patients",title="Male Patients By Cohort and Race/Ethnicity")
graph_CLD$labels$fill <- "Race/Ethnicity"
graph_CLD
```
```{r}
graph_CLD = ggplot(data=combine2,aes(x=Tag,y=sum_Female, fill=race_ethnicity))+
         geom_bar(stat="identity")+theme_bw()+labs(x="Cohort",y="Proportion of Female Patients",title="Female Patients By Cohort and Race/Ethnicity")
graph_CLD$labels$fill <- "Race/Ethnicity"
graph_CLD
```
```{r}
age_N3C = N3C_tags[c("age_at_covid","race_ethnicity")]
age_N3C["Cohort"] = "UVA Data TD"
age_UVA = UVA_tags[c("age_at_covid","race_ethnicity")]
age_UVA["Cohort"] = "UVA Data PD"
age_overall = rbind(age_N3C,age_UVA)
age_overall$race_ethnicity = replace(age_overall$race_ethnicity, age_overall$race_ethnicity=="Asian Non-Hispanic","Asian NH") 
age_overall$race_ethnicity = replace(age_overall$race_ethnicity, age_overall$race_ethnicity=="Black or African American Non-Hispanic","Black/AA NH") 
age_overall$race_ethnicity = replace(age_overall$race_ethnicity, age_overall$race_ethnicity=="White Non-Hispanic","White NH") 
ggplot(age_overall,aes(x=race_ethnicity,y=age_at_covid,fill=Cohort))+geom_boxplot(outlier.colour="back",outlier.shape=16,outlier.size=2,notch=TRUE)+labs(x="Race/Ethnicity",y="Age at COVID Diagnosis",title="Distribution of Ages for UVA Data by Race")+theme_bw()
```


```{r}
colnames(N3C_tags)
```





